---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = TRUE
)
```
# wikiaves

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/wikiaves)](https://CRAN.R-project.org/package=wikiaves)
[![Travis build status](https://travis-ci.org/Athospd/wikiaves.svg?branch=master)](https://travis-ci.org/Athospd/wikiaves)
[![Codecov test coverage](https://codecov.io/gh/Athospd/wikiaves/branch/master/graph/badge.svg)](https://codecov.io/gh/Athospd/wikiaves?branch=master)
<!-- badges: end -->

Non-official R interface for [wikiaves](wikiaves.com.br) API, that retrieve sounds from its repository (no images supported yet). 
The goal of wikiaves R package is to aid analysis and data-driven projects.

**Attention** This package is on a VERY EARLY development stage. Expect things to change a lot! And any help is wellcome =).

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("Athospd/wikiaves")
```

The released version of wikiaves from [CRAN](https://CRAN.R-project.org) will be available soon.


## Example

This is a basic example which shows you how to fetch metadata from registers in wikiaves:

```{r example1, message=FALSE, warning=FALSE}
library(wikiaves)
library(dplyr)
# fetching metadata in a tidy tibble
birds_metadata <- wa_metadata(c("Querula purpurata", "Cotin"))
```

### Downloading... 

This is smart enough to download non-existing or zero sized files only.

```{r example2}
# download mp3
my_mp3_folder <- tempdir()
birds_metadata %>% wa_download(my_mp3_folder)
```

### MP3 files in your local machine with names ready to analytics.

```{r}
head(list.files(my_mp3_folder))
```

### Metadata in a tidy tibble.

```{r}
glimpse(birds_metadata)
```

## Acknowledgement

This package is part of a larger project called **"Automatic acoustic detectors of night bird species in their natural biome"**, oriented by Professor Doctor Linilson Padovese and co-oriented by Professor Doctor Paulo Hubert. This project aims to build machine learning systems in the context of bird identification.

## Contributor Code of Conduct

Please note that the 'wikiaves' project is released with a [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
