---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# wikiaves

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/wikiaves)](https://CRAN.R-project.org/package=wikiaves)
[![Travis build status](https://travis-ci.org/Athospd/wikiaves.svg?branch=master)](https://travis-ci.org/Athospd/wikiaves)
[![Codecov test coverage](https://codecov.io/gh/Athospd/wikiaves/branch/master/graph/badge.svg)](https://codecov.io/gh/Athospd/wikiaves?branch=master)
<!-- badges: end -->

Non-official API of (wikiaves.com.br)[wikiaves.com.br] that retrieves sounds and images from its repository. 
The goal of wikiaves R package is to aid analysis and data-driven projects.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Athospd/wikiaves")
```

The released version of wikiaves from [CRAN](https://CRAN.R-project.org) will be available soon.


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(wikiaves)

# fetching metadata in a tidy tibble
birds_metadata <- wikiaves::wa_metadata(c("Querula purpurata", "Cotin"))

# download mp3
my_mp3_folder <- tempdir()
birds_metadata %>% wa_download(my_mp3_folder)
```

## Contributor Code of Conduct

Please note that the 'wikiaves' project is released with a [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
