---
title: "wikiaves"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{wikiaves}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = TRUE
)
```

The main function is `wa_metadata()`. It takes a "term" specifying the species that you would like to retrieve information and download the audio files (in mp3 format). In the exmaple below brings all records from species "Querula purpurata" into a tidy tibble.

```{r setup, message=FALSE, warning=FALSE}
library(wikiaves)
library(dplyr)
# fetching metadata in a tidy tibble
querula_purpurata_metadata <- wa_metadata(c("Querula purpurata"))
```

```{r}
querula_purpurata_metadata %>% head
```

To download all files from `querula_purpurata_metadata` we could use `wa_download()`.

```{r}
querula_purpurata_metadata %>% wa_download(tempdir())
```

The term could be part of the species name also (like the gender).

```{r}
querula_metadata <- wa_metadata(c("Querula"))
```

For now, to browse for species names is recommended to start from the [wikiaves](wikiaves.com.br) website.
